---
title: "housing"
author: "Ilya"
date: "12/8/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


####install packages
```{r packages, echo=FALSE}
pkgTest <- function(x)
{
  if (x %in% rownames(installed.packages()) == FALSE) {
    install.packages(x, dependencies= TRUE)    
  }
  library(x, character.only = TRUE)
}
neededPackages <- c("leaflet", "raster", "mapview", "sp", "zipcode", "ggmap")

for (package in neededPackages){pkgTest(package)}

```


#Zillow data -- single family homes, zip code -- more lines of this than for neighborhood so perhaps this is smaller spatial scale 
```{r}
Z= read.csv("Zip_Zhvi_SingleFamilyResidence.csv")
names(Z)
#dim(Z)
Z$RegionID = as.character(Z$RegionID)
head(unique(Z$RegionID))#these look like zip codes

#read in zipcode data
zip = data(zipcode)

zipcode = zipcode[c("zip", "latitude", "longitude")]

names(zipcode)[names(zipcode)=="zip"]="RegionID"
dim(Z)[1]
missing_in_zipcode = setdiff(Z$RegionID, zipcode$RegionID)
head(sort(missing_in_zipcode))
Z = merge(Z, zipcode, by = "RegionID")
dim(Z)[1]

not_na_indslat = which(!is.na(Z$longitude))#remove na inds
not_na_indslon = which(!is.na(Z$latitude))#remove na inds
not_na_inds = intersect(not_na_indslon, not_na_indslat)
Z = Z[not_na_inds,]

# df = Z
# proj  = "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
# xy <- cbind(df$longitude,df$latitude)#package sp
# 
# df <-SpatialPointsDataFrame(coords = xy, data = df, 
#                             proj4string = CRS(proj))

#check that zipcodes in zipcode dataset look right
p <-ggplot()+
  geom_point(aes(x = longitude, y = latitude), data = zipcode,  col = "orange",
             alpha = 0.4)
p
missing_zips = setdiff(zipcode$RegionID, Z$RegionID)
length(missing_zips)
#Zillow data seems to be missing a lot of zip codes, unless I am missing something

p <-ggplot()+
  geom_point(aes(x = longitude, y = latitude), data = Z,  col = "orange",
             alpha = 0.4, fill = Z$X2018.08)+
  scale_size_continuous(range = range(Z$X2018.08))
p


#https://blog.dominodatalab.com/geographic-visualization-with-rs-ggmaps/
##I seem to be over query limit so below doesn't work
#usa_center = as.numeric(geocode("United States"))
 
#USAMap = ggmap(get_googlemap(center=usa_center, scale=2, zoom=4), extent="normal")

##commenting out this part of using leaflet to make map
# pal <- colorNumeric("viridis", NULL)
# #commenting this out because it does not display well in github_document
# M<- leaflet(df) %>%
#   addTiles() %>%
#   addCircleMarkers(color = ~pal(X2018.08),
#     stroke = FALSE, fillOpacity = 0.1) %>%
#   # setView(lat = 39.5, lng=-98.5, zoom =4) %>%
#    #  add(stroke = FALSE, smoothFactor = 0.3, fillOpacity = 1,
#    #  fillColor = ~pal(outC$incidence),
#    #  #label with county name 
#    #  label = ~paste0(county_name, ": ", formatC(outC$incidence, big.mark = ","))) %>%
#    addLegend(pal = pal, values = df$X2018.08, opacity = 1.0,
#      labFormat = labelFormat(transform = function(x) round(10^x)))
# 
# # mapshot(M, file = "EMPRESi_cases.png")
# M



```

##Zillow all homes, neighborhood scale (not sure whether this is smaller or larger spatial scale than zip code)
###would be necessary to use Zillow boundaries files to make sense of this neighborhood data: https://www.zillow.com/howto/api/neighborhood-boundaries.htm
```{r}

Z_nh = read.csv("Neighborhood_Zhvi_SingleFamilyResidence.csv")
# names(Z_nh)
dim(Z_nh)
# summary(Z_nh)
```

###now try American Housing Survey data
###https://www.census.gov/programs-surveys/ahs/data/2017/ahs-2017-public-use-file--puf-/ahs-2017-national-public-use-file--puf-.html
```{r}
path = "AHS 2017 National PUF v1.1 CSV/"
A =  read.csv(paste0(path,"household.csv"), skip = 1,
              row.names = 1, header= TRUE)
names(A)
```

